The Driving Forces Behind API Evolution

### 2015-05-18 thesis/paper.tex
Title
Restructured results

\title{The Types and Driving Forces of Modifications in the Evolution of an API}

@@

\subsection{RQ1 Results} \label{results_rq1}
%Re-write this intro a bit (since I moved it)
All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. Table \ref{table:type_counts} shows the total count of each type of change found in the different versions of the API.

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{l|c|c}
              \toprule

              \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
              Enhancive            & 7                         & -                         \\ \hline
              Corrective           & -                         & -                         \\ \hline
              Reductive            & 1                         & -                         \\ \hline
              Adaptive             & 1                         & -                         \\ \hline
              Performance          & -                         & -                         \\ \hline
              Preventive           & 2                         & -                         \\ \hline
              Groomative           & -                         & 5                         \\ \hline
              Updative             & 1                         & 1                         \\ \hline
              Reformative          & 1                         & 1                         \\ \hline
              Evaluative           & -                         & -                         \\ \hline
              Consultive           & -                         & -                         \\ \hline
              Training             & -                         & -                         \\

       \end{tabular}
       \caption{Identified Types of Change}
       \label{table:type_counts}
\end{table}

@@

\subsection{RQ2 Results} \label{results_RQ2} 
\noindent
RQ2: \textbf{How do APIs ``passively'' evolve?}
\smallskip

              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
              Continuing Change                         & True                      \\ \hline
              Increasing Complexity                     & True                     \\ \hline
              Self Regulation                           & True                      \\ \hline
              Conservation of Organisational Stability  & False                     \\ \hline
              Conservation of Familiarity               & True                      \\ \hline
              Continuing Growth                         & True                      \\ \hline
              Declining Quality                         & True                     \\ \hline
              Feedback System                           & True                      \\

       \end{tabular}
       \caption{The applicability of Lehman's laws}
       \label{table:lehman}
\end{table}

\subsubsection{Lehman's Laws}

>>>>

\title{The Driving Forces Behind API Evolution}

@@

\subsection{RQ1 Results} \label{results_rq1}
%Lehman Intro

%Lehman Table
% \begin{table}
%        \centering
%        \begin{tabular}[ht]{l|c}
%               \toprule

%               \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
%               Continuing Change                         & True                      \\ \hline
%               Increasing Complexity                     & True                     \\ \hline
%               Self Regulation                           & True                      \\ \hline
%               Conservation of Organisational Stability  & False                     \\ \hline
%               Conservation of Familiarity               & True                      \\ \hline
%               Continuing Growth                         & True                      \\ \hline
%               Declining Quality                         & True                     \\ \hline
%               Feedback System                           & True                      \\

%               \bottomrule

%        \end{tabular}
%        \caption{The applicability of Lehman's laws}
%        \label{table:lehman}
% \end{table}

%Re-write this intro a bit (since I moved it)
All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. Table \ref{table:type_counts} shows the total count of each type of change found in the different versions of the API.

@@

% \begin{table}
%        \centering
%        \begin{tabular}[ht]{l|c|c}
%               \toprule

%               \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
%               Enhancive            & 7                         & -                         \\ \hline
%               Corrective           & -                         & -                         \\ \hline
%               Reductive            & 1                         & -                         \\ \hline
%               Adaptive             & 1                         & -                         \\ \hline
%               Performance          & -                         & -                         \\ \hline
%               Preventive           & 2                         & -                         \\ \hline
%               Groomative           & -                         & 5                         \\ \hline
%               Updative             & 1                         & 1                         \\ \hline
%               Reformative          & 1                         & 1                         \\ \hline
%               Evaluative           & -                         & -                         \\ \hline
%               Consultive           & -                         & -                         \\ \hline
%               Training             & -                         & -                         \\

%               \bottomrule

%        \end{tabular}
%        \caption{Identified Types of Change}
%        \label{table:type_counts}
% \end{table}

\subsubsection{Types 1by1}

@@

\subsubsection{Laws 1by1}
